Methods for Large Scale Learning to Rank

### 2014-04-11 report/Chapters/AppendixA.tex
graffito + begin benchmark_results.csv
\ac{ -> \acs{ in tabel

\begin{table}
\scalebox{0.87}{
\begin{tabular}{p{0.29cm}|p{7.26cm}||p{0.29cm}|p{9.55cm}}
 \textbf{ID} & \textbf{Feature Description} & \textbf{ID} & \textbf{Feature Description}\\ 
 \hline
1 & \ac{TF} of body					& 36& LMIR.JM of body\\
2 &	\ac{TF} of anchor				& 37& LMIR.JM of anchor\\
3 & \ac{TF} of title				& 38& LMIR.JM of title\\
4 & \ac{TF} of \ac{URL}				& 39& LMIR.JM of \ac{URL}\\
5 & \ac{TF} of whole document		& 40& LMIR.JM of whole document\\

6 & \ac{IDF} of body 				& 41& Sitemap based term propagation\\
7 & \ac{IDF} of anchor 				& 42& Sitemap based score propagation\\
8 & \ac{IDF} of title 				& 43& Hyperlink based score propagation: weighted in-link\\
9 & \ac{IDF} of \ac{URL} 			& 44& Hyperlink based score propagation: weighted out-link\\
10& \ac{IDF} of whole document 		& 45& Hyperlink based score propagation: uniform out-link\\

11& \ac{TF-IDF} of body 			& 46& Hyperlink based feature propagation: weighted in-link\\
12& \ac{TF-IDF} of anchor 			& 47& Hyperlink based feature propagation: weighted out-link\\
13& \ac{TF-IDF} of title 			& 48& Hyperlink based feature propagation: uniform out-link\\
14& \ac{TF-IDF} of \ac{URL}			& 49& HITS authority\\
15& \ac{TF-IDF} of whole document	& 50& HITS hub\\

16& Document length of body			& 51& PageRank\\
17& Document length of anchor		& 52& HostRank\\
18& Document length of title		& 53& Topical PageRank\\
19& Document length of \ac{URL}		& 54& Topical HITS authority\\
20& Document length of whole document	& 55& Topical HITS hub\\

21& BM25 of body					& 56& In-link number\\
22& BM25 of anchor					& 57& Out-link number\\
23& BM25 of title					& 58& Number of slashes in \ac{URL}\\
24& BM25 of \ac{URL}				& 59& Length of \ac{URL}\\
25& BM25 of whole document			& 60& Number of child page\\

26& LMIR.ABS \cite{Zhai2001} of body	& 61& BM25 of extracted title\\
27& LMIR.ABS of anchor				& 62& LMIR.ABS of extracted title\\
28& LMIR.ABS of title				& 63& LMIR.DIR of extracted title\\
29& LMIR.ABS of \ac{URL}			& 64& LMIR.JM of extracted title\\
30& LMIR.ABS of whole document\\

31& LMIR.DIR of body\\
32& LMIR.DIR of anchor\\
33& LMIR.DIR of title\\
34& LMIR.DIR of \ac{URL}\\
35& LMIR.DIR of whole document\\
\end{tabular}
}
\caption{Features of the LETOR .GOV dataset, obtained from Qin et al \cite{Qin2010}}
\label{tbl:features_gov}
\end{table}

>>>>

\begin{table}
\scalebox{0.87}{
\begin{tabular}{p{0.29cm}|p{7.26cm}||p{0.29cm}|p{9.55cm}}
 \textbf{ID} & \textbf{Feature Description} & \textbf{ID} & \textbf{Feature Description}\\ 
 \hline
1 & \acs{TF} of body					& 36& LMIR.JM of body\\
2 &	\acs{TF} of anchor				& 37& LMIR.JM of anchor\\
3 & \acs{TF} of title				& 38& LMIR.JM of title\\
4 & \acs{TF} of \acs{URL}				& 39& LMIR.JM of \acs{URL}\\
5 & \acs{TF} of whole document		& 40& LMIR.JM of whole document\\

6 & \acs{IDF} of body 				& 41& Sitemap based term propagation\\
7 & \acs{IDF} of anchor 				& 42& Sitemap based score propagation\\
8 & \acs{IDF} of title 				& 43& Hyperlink based score propagation: weighted in-link\\
9 & \acs{IDF} of \acs{URL} 			& 44& Hyperlink based score propagation: weighted out-link\\
10& \acs{IDF} of whole document 		& 45& Hyperlink based score propagation: uniform out-link\\

11& \acs{TF-IDF} of body 			& 46& Hyperlink based feature propagation: weighted in-link\\
12& \acs{TF-IDF} of anchor 			& 47& Hyperlink based feature propagation: weighted out-link\\
13& \acs{TF-IDF} of title 			& 48& Hyperlink based feature propagation: uniform out-link\\
14& \acs{TF-IDF} of \acs{URL}			& 49& HITS authority\\
15& \acs{TF-IDF} of whole document	& 50& HITS hub\\

16& Document length of body			& 51& PageRank\\
17& Document length of anchor		& 52& HostRank\\
18& Document length of title		& 53& Topical PageRank\\
19& Document length of \acs{URL}		& 54& Topical HITS authority\\
20& Document length of whole document	& 55& Topical HITS hub\\

21& BM25 of body					& 56& In-link number\\
22& BM25 of anchor					& 57& Out-link number\\
23& BM25 of title					& 58& Number of slashes in \acs{URL}\\
24& BM25 of \acs{URL}				& 59& Length of \acs{URL}\\
25& BM25 of whole document			& 60& Number of child page\\

26& LMIR.ABS \cite{Zhai2001} of body	& 61& BM25 of extracted title\\
27& LMIR.ABS of anchor				& 62& LMIR.ABS of extracted title\\
28& LMIR.ABS of title				& 63& LMIR.DIR of extracted title\\
29& LMIR.ABS of \acs{URL}			& 64& LMIR.JM of extracted title\\
30& LMIR.ABS of whole document\\

31& LMIR.DIR of body\\
32& LMIR.DIR of anchor\\
33& LMIR.DIR of title\\
34& LMIR.DIR of \acs{URL}\\
35& LMIR.DIR of whole document\\
\end{tabular}
}
\caption{Features of the LETOR .GOV dataset, obtained from Qin et al \cite{Qin2010}}
\label{tbl:features_gov}
\end{table}
